\vskip-0.6in \Large Political Uncertainty

### 2016-02-04 GS-extension.tex
add intuition for which legislator is first lobbied

\vskip.2in
Pattern more or less is to get the guy who is WHAT?
\begin{itemize}
	\item Imagine a see-saw; these guys are weights on the see-saw.
\end{itemize}

>>>>

\vskip.2in
Pattern more or less is to get the guy who is WHAT?
\begin{itemize}
	\item Frank: Imagine a see-saw; these guys are weights on the see-saw.
	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote)
\end{itemize}
